Latitudinal gradients in biotic niche breadth vary across ecosystem types

### 2018-08-28 manuscript/correction.tex
going to send the letter back to Daniel

    A subset of food webs analysed for this manuscript (75 out of 263; see \emph{Table S2, Appendix S1} for details) had formatting errors or irregularities that caused them to be incorrectly processed by our original code. We have corrected these inconsistencies and repeated our analyses to ensure that our conclusions did not change. After re-analysis, our results were qualitatively identical to those originally published and our original conclusions hold. However, the specific values given in the results and discussion are now incorrect. Below, we present the results and the relevant portion of the discussion with the original values (struck-through) and corrected values (bold) side by side as well as the original and corrected Figures 2-3.  All supplemental figures have also been updated; as with the main-text figures below, any differences were minor. Reference numbers are as in the original main text.

>>>>

    A subset of food webs analysed for this manuscript (75 out of 263; see \emph{Table S2, Appendix S1} for details) had formatting errors or irregularities that caused them to be incorrectly processed by our original code. Some food webs had inconsistent labels that prevented sets of predators and prey from being correctly linked to the same species. Others listed interactions using categorical symbols; these interactions were not included in our original analyses.

    We have corrected these inconsistencies and repeated our analyses to ensure that our conclusions did not change. After re-analysis, our results were qualitatively identical to those originally published and our original conclusions hold. However, the specific values for correlations and scaling relationships given in the original results and discussion are incorrect. Below, we present the results and the relevant portion of the discussion with the original values (struck-through) and corrected values (bold) side by side as well as the original and corrected Figures 2-3.  All supplemental figures have also been updated; as with the main-text figures below, any differences were minor. Reference numbers are as in the original main text.

### 2018-08-28 manuscript/erratum_letter.tex
going to send the letter back to Daniel

Recently I have revisited the dataset used in this article and noticed that 75  of the webs we used (out of a sample of 263) have irregularities or errors of formatting that caused them to be incorrectly processed by our original code. Fortunately, after repeating all analyses with corrected versions of these 75 webs our results were qualitatively identical to those published and our conclusions remain unchanged. Unfortunately, the specific values given in the published text are nearly all incorrect.

I have attached a corrected version of the results and a small portion of the discussion with the original values struck through and the corrected values provided side-by-side. No further changes to the manuscript were necessary. I hope that this demonstrates that our conclusions hold and will be suitable as a corrigendum for our manuscript. I have also attached an updated supplemental information document which now includes a table (Table S2) giving details of the webs which required corrections.

My co-authors and I deeply regret not finding and correcting these errors earlier, and appreciate your kind attention in this matter.

>>>>

As requested, we have revised our correction by adding a section to explicitly state the purpose of the correction. In this description we refer to \emph{Table S2}, which details the food webs that were corrected and the reason for the correction. We agree with the Editor that our previous submission required a lot of effort from a reader; we had used the ''Original text'', ''Revised text'' format in response to a specific request when we first attempted to submit the correction. In the absence of any guidelines as to how corrections should be formatted, we hope that our current approach will be more user-friendly. We give the results and discussion only once, with original values presented in struck-through font and corrected values immediately following in bold. We believe that this will allow readers to see at a glance that the changes to our results are quite minor.

Thank you again for considering this correction. My co-authors and I are glad to have the opportunity to fix our manuscript and preserve the high quality of research presented in \textbf{Proceedings of the Royal Society B}.
